Modeling trend in temperature volatility using generalized LASSO

### 2018-05-16 nips-2018/paper.tex
update paper

for $w>0$, where $\mu_1$ and $\mu_2$ are dual variables for the
$\ell_\infty$ constraint, as $w\rightarrow\infty$,
the solution to this nonlinear system reduces to the KKT
conditions. Therefore, the PDIP method takes Newton steps to solve the
system for a series of increasing values of $w$. \autoref{alg:pdip}
provides the details. 
\begin{algorithm}[tb]
  \caption{PDIP for $\ell_1$ variance estimation}
  \label{alg:pdip}
  \begin{algorithmic}
    \REQUIRE $\lambda>0$, $w>0$, $\nu\leftarrow 0$, $\mu_1\leftarrow
    0$, $\mu_2\leftarrow 0$, $J\in\mathbb{Z}^+$, $\{w_k\}$
    \COMMENT{Initialization} 
    \FOR[Central path]{$k=1,2,\ldots$}
    \FOR[Newton updates]{$j=1,\ldots,J$}
    \STATE Solve $A [\Delta\nu\; \Delta\mu_1\; \Delta\mu_2]^\top=r_{w_k}$ to find the search direction.
    \STATE $\quad\quad A$ is the Jacobian of $r_w$ in \eqref{eq:resid}.
    \STATE Update $[\nu^{j+1}\; \mu^{j+1}_1\; \mu^{j+1}_2] \leftarrow
    [\nu^{j}\; \mu^{j}_1\; \mu^{j}_2] + [\Delta\nu\; \Delta\mu_1\;
    \Delta\mu_2]$. 
    \ENDFOR
   \ENDFOR
   \RETURN $h=\log\frac{y^2}{1+D^\top\nu}$ \attn{Is this right?
     Explicit form of $A$}
  \end{algorithmic}
\end{algorithm}

@@

By this definition of $x_i$, the update step for $x_i$ is the
following optimization problem: $x_i^{m+1}:=\argmin_{x_i} ( f_i(x_i) +
(u_i^m)^\top x_i + (\rho/2) \lVert x_i-\tilde{z}_i^m \lVert_2^2)$. We solve this using the PDIP method. As it was explained in \autoref{sec:l1tf_var}, to use PDIP we need to compute the dual problem, which in turn needs the computation of the Fenchel conjugate of the loss function. In addition, referring to \autoref{alg:pdip}, we need to compute the gradient and Jacobian of the conjugate functions. It is important to note that compare to the optimization problem \autoref{eq:l1tf_var}, the loss function in the x-update step in \autoref{eq:ADMM_steps} includes the quadratic term $(\rho/2) \lVert x_i-\tilde{z}_i^m \lVert_2^2$. This makes the computation more involved than \autoref{sec:l1tf_var}. The details of the computations are explained in Appendix 1.

@@

\begin{theorem}
  Let $f(h) = \sum_{k} h_{k} + y_{k}^2e^{-h_{k}}$ and $g(x) =
  \norm{x}_1$. Then, 
  \begin{align}
    [\prox_{\mu f}(u)]_k &= \mathscr{W}\bigg(\frac{y_k^2}{\mu}
    \exp\bigg(\frac{1-\mu u_k}{\mu}\bigg) \bigg) + \frac{1-\mu u_k}{\mu},\\
    \prox_{\rho g}(u) &= S_{\rho\lambda}(u)
  \end{align}
where $[S_{\alpha}(u)]_k = \sign(u_k)(|u_k| -\alpha_k)_+$ and
$(v)_+=v\vee 0$.
\end{theorem}
\begin{proof}
  If $f(x)=\sum_k f_k(x_k)$ then $[\prox_{\mu f}(x)]_k =
  \prox_{\mu f_k}(u_k)$. So 
  $[\prox_{\mu f}(u)]_k=\min_{x_k} \,\,
  \mu\big(x_k+y_{k}^2e^{-x_{k}}\big)+\frac{1}{2}  (x_k-u_k)^2.$
  Setting the derivative to 0 and solving for $u_k$ gives the
  result. Similarly, $[\prox_{\rho g}(u)]_\ell=\rho
  \lambda_\ell |z_\ell|+1/2(z_\ell-u_\ell)^2$. This is not differentiable,
  but the solution must satisfy $\rho \cdot \lambda_\ell \cdot \partial
  \big(|z_\ell| \big)=u_\ell-z_\ell$ where $\partial \big(|z_\ell| \big)$ is the
  sub-differential of $|z_\ell|$. The solution is the soft-thresholding
  operator $S_{\rho\lambda_\ell}(u_\ell)$.
\end{proof}

@@

\section{Appendix}

\attn{put this in nips appendix format}

>>>>

for $w>0$, where $\mu_1$ and $\mu_2$ are dual variables for the
$\ell_\infty$ constraint, as $w\rightarrow\infty$,
the solution to this nonlinear system reduces to the Karush–Kuhn–Tucker (KKT)
conditions. Therefore, the PDIP method takes Newton steps to solve the
system for a series of increasing values of $w$. \autoref{alg:pdip}
provides the details.

\begin{algorithm}[tb]
  \caption{PDIP for $\ell_1$ variance estimation}
  \label{alg:pdip}
  \begin{algorithmic}
    \REQUIRE $\lambda>0$, $w>0$, $\nu\leftarrow 0$, $\mu_1\leftarrow
    0$, $\mu_2\leftarrow 0$, $J\in\mathbb{Z}^+$, $\{w_k\}$
    \COMMENT{Initialization} 
    \FOR[Central path]{$k=1,2,\ldots$}
    \FOR[Newton updates]{$j=1,\ldots,J$}
    \STATE Solve $A [\Delta\nu\; \Delta\mu_1\; \Delta\mu_2]^\top=r_{w_k}$ to find the search direction.
    \STATE $\quad\quad A$ is the Jacobian of $r_w$ in \eqref{eq:resid}.
    \STATE Update $[\nu^{j+1}\; \mu^{j+1}_1\; \mu^{j+1}_2] \leftarrow
    [\nu^{j}\; \mu^{j}_1\; \mu^{j}_2] + [\Delta\nu\; \Delta\mu_1\;
    \Delta\mu_2]$. 
    \ENDFOR
   \ENDFOR
   \RETURN $h=\log\frac{y^2}{1+D^\top\nu}$ \attn{Is this right?
     Explicit form of $A$}
  \end{algorithmic}
\end{algorithm}

@@

By this definition of $x_i$, the update step for $x_i$ is the
following optimization problem: $x_i^{m+1}:=\argmin_{x_i} ( f_i(x_i) +
(u_i^m)^\top x_i + (\rho/2) \lVert x_i-\tilde{z}_i^m \lVert_2^2)$. We solve this using the PDIP method. As it was explained in \autoref{sec:l1tf_var}, to use PDIP we need to compute the dual problem, which in turn needs the computation of the Fenchel conjugate of the loss function. In addition, referring to \autoref{alg:pdip}, we need to compute the gradient and Jacobian of the conjugate functions. It is important to note that compare to the optimization problem \autoref{eq:l1tf_var}, the loss function in the x-update step in \autoref{eq:ADMM_steps} includes the quadratic term $(\rho/2) \lVert x_i-\tilde{z}_i^m \lVert_2^2$. This makes the computation more involved than \autoref{sec:l1tf_var}. The details of the computations are explained in \autoref{sec:app_consADMM}.\attn{change this to appendix}

@@

\begin{theorem}
  Let $f(h) = \sum_{k} h_{k} + y_{k}^2e^{-h_{k}}$ and $g(x) =
  \norm{x}_1$. Then, 
  \begin{align}
    [\prox_{\mu f}(u)]_k &= \mathscr{W}\bigg(\frac{y_k^2}{\mu}
    \exp\bigg(\frac{1-\mu u_k}{\mu}\bigg) \bigg) + \frac{1-\mu u_k}{\mu},\\
    \prox_{\rho g}(u) &= S_{\rho\lambda}(u)
  \end{align}
where $\mathscr{W}(\cdot)$ is the \textit{Lambert function} \cite{corless_lambertw_1996},  $[S_{\alpha}(u)]_k = \sign(u_k)(|u_k| -\alpha_k)_+$ and
$(v)_+=v\vee 0$.
\end{theorem}
\begin{proof}
  If $f(x)=\sum_k f_k(x_k)$ then $[\prox_{\mu f}(x)]_k =
  \prox_{\mu f_k}(u_k)$. So 
  $[\prox_{\mu f}(u)]_k=\min_{x_k} \,\,
  \mu\big(x_k+y_{k}^2e^{-x_{k}}\big)+\frac{1}{2}  (x_k-u_k)^2.$
  Setting the derivative to 0 and solving for $u_k$ gives the
  result. Similarly, $[\prox_{\rho g}(u)]_\ell=\rho
  \lambda_\ell |z_\ell|+1/2(z_\ell-u_\ell)^2$. This is not differentiable,
  but the solution must satisfy $\rho \cdot \lambda_\ell \cdot \partial
  \big(|z_\ell| \big)=u_\ell-z_\ell$ where $\partial \big(|z_\ell| \big)$ is the
  sub-differential of $|z_\ell|$. The solution is the soft-thresholding
  operator $S_{\rho\lambda_\ell}(u_\ell)$.
\end{proof}

@@

\section{Appendix A}
\label{sec:app_l1tf_var}

In this appendix we provide more details on how to solve the optimization problem \ref{eq:l1tf_var}

\section{Appendix B}
\label{sec:app_consADMM}
\attn{put this in nips appendix format}
